The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals

### 2021-02-02 publications/2020-03-paper/credit-statements/credit.tex
separates credit statement, declaration of interest based on applied energy guidelines
Former-commit-id: 15bdec437b737268ef40dcbb97979ba5d996b60a
Former-commit-id: c1132ae75c7fe5215b0927d3a86a69bc7c6786ca

\begin{document}
\begin{frontmatter}
\title{The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
	\item Identifies potential transition pathways for Japan using multiple technologies.
	\item Simulations to the year 2100 identify post-2050 impacts of a stabilizing transition. 
	\item Dynamic simulations use learning curves for cost and emissions.
	\item Sensitivity analysis identifies key parameters, thresholds, and trade-offs.
\end{itemize}
\end{document}

>>>>

\begin{document}
\begin{frontmatter}
\title{The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals}
\end{frontmatter}
\section*{CRediT Statement}

The authors contributed to this work as described below.

\textbf{Anshuman Chaube}: Methodology, validation, writing - original draft, visualisation.

\textbf{Andrew Chapman}: Methodology, validation,  writing - original draft, writing - review and editing.

\textbf{Akari Minami}: data curation, validation.

\textbf{James Stubbins}: writing - review and editing, supervision.

\textbf{Kathryn D. Huff}: Conceptualisation, resources, writing - review and editing, supervision.
\end{document}

### 2021-02-02 publications/2020-03-paper/declaration-of-interests/declaration.tex
separates credit statement, declaration of interest based on applied energy guidelines
Former-commit-id: 15bdec437b737268ef40dcbb97979ba5d996b60a
Former-commit-id: c1132ae75c7fe5215b0927d3a86a69bc7c6786ca

\begin{document}
\begin{frontmatter}
\title{The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals}
\end{frontmatter}
\section*{CRediT Statement}

The authors contributed to this work as described below.

\textbf{Anshuman Chaube}: Methodology, validation, writing - original draft, visualisation.

\textbf{Andrew Chapman}: Methodology, validation,  writing - original draft, writing - review and editing.

\textbf{Akari Minami}: data curation, validation.

\textbf{James Stubbins}: writing - review and editing, supervision.

\textbf{Kathryn D. Huff}: Conceptualisation, resources, writing - review and editing, supervision.
\end{document}

>>>>

\begin{document}
\begin{frontmatter}
\title{The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals}
\end{frontmatter}
\section*{Declaration of interests}
The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.\end{document}
